Automated detection \& characterization of long-period transits in the \kepler\ archive

### 2015-12-23 document/ms.tex
document structure

\newcommand{\uw}{3}
\newcommand{\nyu}{4}
\newcommand{\cds}{5}
\newcommand{\mpia}{6}
\newcommand{\mpis}{7}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,2,\uw},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@uw.edu}}
\altaffiltext{2}         {Sagan Fellow}
\altaffiltext{\uw}       {Astronomy Department, University of Washington,
                          Seattle, WA, 98195, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\cds}      {Center for Data Science, New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

@@

@@

@@

>>>>

\newcommand{\uw}{3}
\newcommand{\nyu}{4}
\newcommand{\cds}{5}
\newcommand{\mpia}{6}
\newcommand{\mpis}{7}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,2,\uw},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    and others
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@uw.edu}}
\altaffiltext{2}         {Sagan Fellow}
\altaffiltext{\uw}       {Astronomy Department, University of Washington,
                          Seattle, WA, 98195, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\cds}      {Center for Data Science, New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

@@

\section{Single transit search}

Previous automated searches for transits in the \kepler\ light
curves have restricted their results to candidates with at least three
observable transits in the dataset.
This restriction minimizes contamination by false alarms at low
signal-to-noise.
Noise in the light curves introduced by stellar or instrumental variability
can easily masquerade as a small planet with a long orbital period and lead to

@@

We start with the PDC-MAP light curves downloaded from
MAST\footnote{\url{https://archive.stsci.edu/kepler/}}.

@@

\section{Candidate vetting}

\paragraph{Light curve}

Blah.

\paragraph{Pixel-level}

Blah.

\paragraph{Auxiliary data}

Blah.

\section{Results}

\section{Completeness \& reliability}
